Environmental stress drives plant and pollinator specialisation

### 2020-06-17 paper/manuscript.Rmd
Actual and potential number of partners aren't actually that close
Updates to intro based on Chris feedback

One possible explanation for the seemingly contradictory evidence is that different bioclimatic factors (like temperature or precipitation) can have contrasting effects on species and their partners, such that we lack a common currency with which to derive general responses to the environment. 
Here we attempt to overcome these barriers to deriving general rules by reducing multiple factors into a single measure of environmental stress. 
Previous research suggests that environmental stress may affect the number of interaction partners a species has in different ways depending on the species' role in the community (for example its trophic guild) [@tylianakis_ecological_2017]. 
Specifically, we propose two alternative hypotheses of how environmental stress may affect specialisation. 
First, species under environmental stress might be "pressured" to focus on partners with which they are best adapted to interact. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, constrained their host use to those with which phylogenetic matching was strongest.
Similarly, @lavandero_genotype_2013 showed that environmental stress due to higher temperature reduced the trophic niche breadth (range of host genotypes used) of parasitoids, suggesting higher specialisation.

@@

Here, we investigate whether and how environmental stress can systematically affect specialisation. 
Our main aim is to test the two hypotheses mentioned above that relate environmental stress with a species' number of partners and investigate whether this changes systematically across species or between trophic guilds. 
We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014]. 
In other words, we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
Species with many partners, conversely, should have a larger pool of available partners and might, therefore, be more likely to specialise on the most beneficial partners under environmental stress. 
Importantly, when testing these hypotheses, we control for the potential effects of the environment on community composition [which has been previously shown to be a determinant factor; @gravel_bringing_2018]. 
We test these hypotheses using data on plant-pollinator interactions. 
These interactions provide a particularly interesting system to test these hypotheses. 
Due to the multiple trade-offs involved in the pollination service, there are several ways in which species could respond to environmental stress given the available partners.
We estimate the stress species might experience in a given community based on the species' patterns of global occurrence.

@@

We evaluated four models to assess the relative importance of stress for each focal species.  
A first model, our baseline model, included five variables. 
<!-- fixed variables (population-level predictors) and two random variables (grouping levels). -->
The predictors in the baseline model were the environmental stress of the community for each focal species, the species' number of known possible partners in the community, and both the species guild (plant or a pollinator) and its interaction with environmental stress.
We included the number of known possible partners as a predictor in our models as it allows us to control for the effects of the environment on community composition, effectively accounting for species co-occurrence. 
We determined the number of possible partners in a particular community by counting the number of species in the opposite guild with which the species interacted in any other community in our interaction dataset.
Controlling for the number of potential partners makes our model a particularly stringent test of our environmental-stress hypotheses because this variable could explain a large proportion of variance. 
Often, the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.

>>>>

One possible explanation for the seemingly contradictory evidence is that different bioclimatic factors (like temperature or precipitation) can have contrasting effects on species and their partners, such that we lack a common currency with which to derive general responses to the environment. 
Here we attempt to overcome these barriers to deriving general rules by reducing multiple factors into a single measure of environmental stress. 
Previous research suggests that environmental stress may affect the number of interaction partners a species has in different ways depending on the species' role in the community (for example its trophic guild) [@tylianakis_ecological_2017]. 
Specifically, we propose two alternative hypotheses of how environmental stress may affect specialisation. 
First, species under environmental stress might be "pressured" to focus on partners with which they are best adapted to interact. 
In other words under environmental stress they are more specialised than otherwise. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes compared to lower altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, constrained their host use to those with which phylogenetic matching was strongest.
Similarly, @lavandero_genotype_2013 showed that environmental stress due to higher temperature reduced the trophic niche breadth (range of host genotypes used) of parasitoids, suggesting higher specialisation.

@@

Here, we investigate whether and how environmental stress can systematically affect specialisation. 
Our main aim is to test the two hypotheses mentioned above that relate environmental stress with a species' number of partners and investigate whether this changes systematically across species or between trophic guilds. 
We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014]. 
In other words, we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
Species with many partners, conversely, should have a larger pool of available partners and might, therefore, be more likely to specialise on the most beneficial partners under environmental stress. 
Importantly, when testing these hypotheses, we control for the potential effects of the environment on community composition [which has been previously shown to be a determinant factor; @gravel_bringing_2018]. 
We test these hypotheses using data on plant-pollinator interactions. 
These interactions provide a particularly interesting system to test these hypotheses. 
Plant-pollinator interactions are loose enough detect a signal of flexibility and partner preference but strong enough to drive coevolutionary processes [@hutchinson_cophylogenetic_2017]. 
We estimate the stress species might experience in a given community based on the species' patterns of global occurrence.

@@

We evaluated four models to assess the relative importance of stress for each focal species.  
A first model, our baseline model, included five variables. 
<!-- fixed variables (population-level predictors) and two random variables (grouping levels). -->
The predictors in the baseline model were the environmental stress of the community for each focal species, the species' number of known possible partners in the community, and both the species guild (plant or a pollinator) and its interaction with environmental stress.
We included the number of known possible partners as a predictor in our models as it allows us to control for the effects of the environment on community composition, effectively accounting for species co-occurrence. 
We determined the number of possible partners in a particular community by counting the number of species in the opposite guild with which the species interacted in any other community in our interaction dataset.
Controlling for the number of potential partners makes our model a particularly stringent test of our environmental-stress hypotheses because this variable could explain a large proportion of variance.
